noTCP: extend, extend, repurpose

### 2014-06-10 paper/paper.tex
table of network characteristics

Urgent pointer is both a good and a bad candidate at the same time: it is already recommended against the use of the urgent mechanism~\cite{Gont:2011vi}, therefore it could be claimed that it is taking up precious space in the TCP header. On the other hand, it is common practice by NIDS to reset the field as it makes it difficult to track the application-layer data~\cite{seolma}. While we witnessed the field to be passed through on many of our studied networks, we also found many that do not (Table...), therefore it is a usable but not our preferred choice.

@@

>>>>

Urgent pointer is both a good and a bad candidate at the same time: it is already recommended against the use of the urgent mechanism~\cite{Gont:2011vi}, therefore it could be claimed that it is taking up precious space in the TCP header. On the other hand, it is common practice by Network Intrusion Detection Systems (NIDS) to reset the field as it makes it difficult to track the application-layer data~\cite{seolma}. We present our observations of how often the field is filtered in Section~\ref{sec:network}, however although we witnessed the field to be passed through on many of our studied networks and hence it is a usable option, it is not without drawbacks.

@@

\section{Network cahracteristics}
\label{sec:network}

In this section we look at the different network behaviours as observed by our testing tool.

\begin{table*}[t]
{\small
\begin{center}
\begin{tabular}{| l | >{\centering\arraybackslash}m{0.8cm} | >{\centering\arraybackslash}m{0.9cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.6cm} | >{\centering\arraybackslash}m{1.6cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.5cm} | >{\centering\arraybackslash}m{1.cm} | }
\hline
    \textbf{Net ID} & \textbf{No filter} & \textbf{Global IP}   & \textbf{Port-specific} & \textbf{Validate checksum} & \textbf{Drop S/A data} & \textbf{Normalize ACK}  & \textbf{Normalize URG} & \textbf{Normalize Reserved} & \textbf{Remap Seq.} \\ \hline \hline
    % Univ Helsinki WiFi
    WiFi education 1 &                   &                      &                        & \checkmark                 &                        &                         &                        &                             &                     \\ \hline
    % Eduroam
    WiFi education 2 &                   & \checkmark           &                        &                            & \checkmark             &                         & \checkmark \checkmark  &                             & \checkmark          \\ \hline
    % wgb
    WiFi public 1      & \checkmark      &                      &                        &                            &                        &                         &                        &                             &                     \\ \hline
    % Finland internet.saunalahti
    Cellular Finland 1 & \checkmark      &                      &                        &                            &                        &                         &                        &                             &                     \\ \hline
    % Virgin home
    WiFi residential 1 &                 &                      &                        & \checkmark                 &                        &                         &                        &                             &                     \\ \hline
    % GiffGaff
    Cellular UK 1      &                 &                      &  \checkmark (443, 993) & -                          & -                      & -                       & -                      & -                           & -                   \\ \hline            
\end{tabular}
\end{center}
}
\caption{Network behaviour observed through tests generating custom TCP packets}
\label{tab:networks}
\end{table*}
